True versus apparent shapes of astrophysical bow shocks

### 2016-06-21 papers/Paper1/sec-application.tex
Add to paper new version of characterstic radii

\begin{figure}
\begin{tabular}{c}
\includegraphics[width=\linewidth]{AB-beta} \\
\includegraphics[width=\linewidth]{thc-beta}
\end{tabular}
\caption{Top:Characteristic radii, normalized with $R_0$ vs $\beta$. In solid line we plot the radius of curvature, while in dashed line we plot $R_{90}$. Bottom: $\theta_c$ vs $\beta$. For
highly anisotropic shells $\xi <0.4$, the resulting shell has shape of an oblate spheroid, while for the isotropic case, the resulting shell is an hyperbola. the proplyd case is noticeable because it has
a transition from spheroidal shapes to hyperbola.
%$\theta_c$, $R_c$ and $R_{90}$ versus $\beta$ for different anisotropy degrees, represented with the $\xi$ paramenter.}
}
\label{fig:rad-beta}
\end{figure}

>>>>

\begin{figure}
\begin{tabular}{c}
\includegraphics[width=\linewidth]{figs/AB-beta-log} \\
\includegraphics[width=\linewidth]{figs/thc-beta-log}
\end{tabular}
\caption{Top: Characteristic radii, $A = R_c/R_0$ (solid lines) and $B
  = R_{90}/R_0$ (dashed lines)
  vs $\beta$, calculated from quadric fits to the generalized CRW
  solutions with varying degrees of isotropy $\xi$.  Bottom: Conic
  angle $\theta_c$ vs $\beta$ for the bow 
  shock head (solid lines) and the bow shock tail (dashed lines).}
\label{fig:rad-beta}
\end{figure}
